Fig3

### 2020-04-13 analysis/figure-3.Rmd
now with hormoens

@@

  x <- candidatevsd %>%
    filter(tissue == whichtissue)  %>%
    pivot_wider(names_from = gene, values_from = counts) %>%
    select(-sex, - tissue, - treatment, -samples) %>%
    correlate()
  print(fashion(x))

>>>>

hormones <- read_csv("../results/07_hormoneswide.csv") %>%
  select(-study, -treatment, -sex)
head(hormones)

head(candidatevsd)

vsdhormones <- candidatevsd %>%
  pivot_wider(names_from = gene, values_from = counts) %>%
  mutate(bird_id = sapply(strsplit(samples,"\\_"), "[", 1)) %>%
  left_join(.,hormones, by =  "bird_id")
vsdhormones

@@

  x <- vsdhormones  %>%
    filter(tissue == whichtissue) %>%
    select(-sex, - tissue, - treatment, -samples, -bird_id, -moltbin) %>%
    correlate()
  print(fashion(x))
